\documentclass{article}
\usepackage{url}
\title{UI Design Milestone 1}
\author{Alex Hart, Dan Levy, Mike McGuire, Corey Young, Jessica Perrie}
\date{\today}
\begin{document}
\maketitle

\section{Use Cases}
\subsection{Meet a Friend}
The user wishes to arrange a place to meet a friend between classes.
The friend has communicated the location of their prior class, and the user
wants to find a meeting place between the friend's class and their own.

To do this, the user opens the Campus Mapper application, and enters the
friend's classroom into the search bar. The application locates the classroom,
and displays a menu with an option to \emph{Show location}. The application
then shows a map centred on the classroom. The user zooms out until their own
classroom is visible (marked by a ``Saved location'' indicator), and chooses a
suitable meeting place between the two. The user can optionally select the
chosen location and send it to their friend via email or SMS.

\subsection{Closest Wireless Hotspot}
The user wishes to connect to the university's wireless network. They would like
to know the location of the nearest wireless hotspot.

The user opens the Campus Mapper application, and hits the Menu button. The
application displays a menu containing a \emph{Find wireless} option.
The user selects \emph{Find wireless}. The application locates the nearest
university wireless hotspot, and presents a menu containing options to
\emph{Show location}, and to \emph{Get directions}. The user may select either
option; \emph{Show location} will show a map centred on the hotspot, \emph{Get
directions} will provide walking directions from the user's location to the
hotspot.

\section{Narratives}
\subsection{Condoleezza}
\subsubsection{What They Do Now (To Find Buildings and Services)}

Because Condoleezza is new to Halifax, she wants to learn as much as possible
about the city and culture. However, Condoleezza is also afraid of getting lost
and missing time to study. Hence to locate buildings or services on campus, she
cross-references multiple online maps and directions from people and online
sources. 

To locate buildings on campus, she uses the Dalhousie online maps (Campus Map
BETA, Sexton Campus Map). In the BETA map she uses the query function to search
for buildings, and the map function to click on building shapes for
more—possibly important—information. She also checks the Sexton Campus Map
because one of her friends suggested it to her, and because it lists only Sexton
Campus buildings—buildings relevant to her study and area. 

To find services on campus, she uses the BETA map by using the “View campus
amenities” menu. She likes to cross-reference the service location with the
Sexton Campus Map.

On arriving closer to the locations or services, she asks friends or complete
random strangers for directions. Sometimes their directions are not clear;
however, they can confirm her location and increase her trustfulness for the
online maps and the community. On approaching her destination, she also looks
for physical signs or maps.

\subsubsection{What They Do in Future With App (To Find Buildings and Services)}

By using the App, Condoleezza can locate buildings on campus by clicking the
building on the map, selecting the location from her favourites, selecting the
building from a list of campus buildings or querying the system. Being able to
contact her friends from the App would decrease the chance that she’d use the
online Sexton Map at a friend’s suggestion—because they are already using to map
function to communicate. Thus the App would be her sole instrument to locate
buildings.

The App would also show her were relevant services were on campus by allowing
her to view a filtered map or use the query function to search for a service.
Additionally, she would use the App to confirm her location within buildings by
observing floor plans instead of only looking for physical signs and taking the
advice of her friends or complete strangers.

\subsubsection{Links}
\begin{itemize}
\item Campus Map BETA \hfill                      \url{http://campusmap.dal.ca/}
\item Sexton Campus Map \\
                      \hfill \url{http://fm.dal.ca/campusmap/index.php?campus=X}
\end{itemize}
\end{document}
